Taking Dyads Seriously

### 2020-06-09 paper/3_sim.tex
additional sim cases

>>>>

x is a vector of observed node-specific characteristics and w is a vector of unobserved node specific characteristics. We draw n values for both from a standard normal. For both x and we we then take the cross-product of their transpose to generate n x n matrices. Values for mu, beta, and gamma are set to -2, 1, and 1, respectively.

### 2020-06-09 paper/6_appendix.tex
additional sim cases

>>>>

\section{Correlation with Omitted Variable}

Things get more challenging when the omitted variable is correlated with the observed variable. In the case of normal linear regression you can show that in general a regression coefficient is unbiased for its "unconditional effect", which is the direct effect plus something related to the direct effects of any omitted variables that it is correlated with. For example, suppose $w_{i,j}$ is correlated with $x_{i,j}$ via the relation $w_{i,j} = \alpha x_{i,j} + z_{i,j}$. Then:

\begin{align*}
y_{i,j} & = \mu + \beta x_{i,j} + \gamma w_{i,j} + \epsilon_{i,j} \\
&= \mu + (\gamma \alpha+\beta ) x_{i,j} + (\gamma z_{i,j} + \epsilon_{i,j})  \\
&= \mu + \tilde \beta x_{i,j} + \tilde \epsilon_{i,j}
\end{align*}

The naive model is in some sense still "correct" as it is an unbiased estimator of the unconditional (direct plus indirect) effect $\gamma\alpha + \beta$ of $x$ on $y$.

As far as I know there is no way to eliminate this extra biased without making further assumptions about the nature of the omitted variable. However, an interesting question is whether or not we can reduce the bias in the network setting by assuming the omitted variable $w_{i,j}$ is the product of latent node-specific factors. An idea related to this is discussed in \citet{minhas:etal:2017:arxiv}.
